Meta-analysis of fungicide efficacy for FHB control in Brazil

### 2017-04-29 fhb-sev.Rmd
Formatting code

@@

# Load packages 
library(tidyverse)
library(metafor)
library(knitr)
library(ggthemes)
library(cowplot)
library(scales)
```

>>>>

```{r}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=80),tidy=TRUE)
```

@@

# Load packages 
library(tidyverse)
library(metafor)
library(ggthemes)
library(cowplot)
library(scales)
```
